%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Batu Bora} \\ \vspace{1pt}
    \small \href{mailto:hello@batubora.com}{hello@batubora.com} $|$ 
    \href{https://github.com/cenab}{\underline{github.com/cenab}} $|$ 
    \href{https://www.linkedin.com/in/cenab/}{\underline{linkedin.com/cenab}} $|$
    \href{http://www.batubora.com}{\underline{batubora.com}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Alberta}{Sep. 2018 -- May 2023}
      {Bachelor of Science in Computer Science}{Edmonton, AB}
      % \resumeItemListStart
      %   \resumeItem{\textbf{Relevant Coursework:} Search Knowledge and Simulation, Reinforcement Learning, Machine Learning, Automata Theory, Parallel and Distributed Systems, AI Capstone, Graph Theory}
      % \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Software Developer}{Mar. 2023 -- Present}
    {Userful Corporation}{Calgary, Alberta}
    \resumeItemListStart
      \resumeItem{Led the end-to-end development of an enterprise SaaS solution utilizing \textbf{ReactJS, TypeScript,} and \textbf{Java Quarkus}.}
      \resumeItem{Directed the development of a core serverless product on \textbf{AWS (Lambda, API Gateway, DynamoDB, SQS)}, optimizing both performance and scalability.}
      \resumeItem{Spearheaded strategic partnerships with \textbf{Microsoft AI} and \textbf{Cisco}, driving joint solution development and expanding enterprise reach.}
      \resumeItem{Fine-tuned large language models for resource-efficient Retrieval Augmented Generation (RAG), significantly improving performance and reducing latency.}
      \resumeItem{Engineered robust data pipelines (\textbf{Airbyte}) for seamless integration with the \textbf{Qdrant vector database}, enhancing search and retrieval capabilities.}
      \resumeItem{Developed advanced media processing solutions in \textbf{Rust}, leveraging \textbf{Gstreamer} and \textbf{FFMPEG}.}
      \resumeItem{Designed and integrated critical pipeline components into the \textbf{CI/CD workflow}, streamlining deployments and ensuring high-quality releases.}
    \resumeItemListEnd

    \resumeSubheading
      {Research Fellow}{Jan. 2025 -- Present}
      {Ege University}{Izmir, Turkey}
      \resumeItemListStart
        \resumeItem{Developed "iShe," a full-stack, real-time conversational AI companion to support individuals with dementia.}
        \resumeItem{Built the client in \textbf{React Native} and the server with \textbf{Express.js} and \textbf{Supabase} (PostgreSQL, pgvector), integrating \textbf{Whisper} and \textbf{OpenAI} to create the AI agent, hosted on \textbf{Microsoft Azure}.}
        \resumeItem{Implemented features including secure authentication, voice/text interaction, vector similarity search for contextual understanding, and conversation history management.}
      \resumeItemListEnd

  \resumeSubheading
    {Teaching Assistant}{Sep. 2022 -- Jan. 2023}
    {Department of Computing Science, University of Alberta}{Edmonton, AB}
    \resumeItemListStart
      \resumeItem{Developed quiz and exam materials on \textbf{Deep Neural Networks}, \textbf{AlphaGo} architecture, and decision-making search algorithms for CMPUT 455.}
      \resumeItem{Provided student support during office hours and contributed to course logistics through weekly TA meetings.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
\resumeSubHeadingListStart
    \resumeItem{\textbf{Languages:} Java, TypeScript, JavaScript, Python, C++}
    \resumeItem{\textbf{Frameworks:} Quarkus, ReactJS, Android, React Native, Django, Flask}
    \resumeItem{\textbf{Databases/DevOps:} SQL, PostgreSQL, Qdrant, LanceDB, Git, NGINX, Linux}
    \resumeItem{\textbf{Infrastructure:} Docker Compose, Kubernetes, Terraform, Microsoft Azure, AWS, Google Cloud Platform}
    \resumeItem{\textbf{ML/AI:} LangChain, Ollama, Quantized LLM models, Celery}
\resumeSubHeadingListEnd
    
%-----------RESEARCH-----------
\section{Publications}
\resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{Network Identity Management: Application, Action and Device Aware Monitoring} $|$ IEEE COMPSAC 2025}{}
        \resumeItemListStart
          \resumeItem{Conceptualized and developed Network Identity Management (NIM), an ML-based system for identity-aware access control in encrypted applications, achieving a 98.6\% F1-score for application and perfect device identification.}
          \resumeItem{Engineered a scalable, cloud-native Android traffic generation framework using \textbf{Google Cloud, Cuttlefish,} and \textbf{ADB}, emulating realistic multi-user, asynchronous group chat behaviors across eight IMAs.}
          \resumeItem{Implemented advanced encrypted traffic analysis, leveraging flow-level metadata and ML models (including \textbf{Gradient Boosting}) to classify applications, devices, and user actions.}
        \resumeItemListEnd
        
    \resumeProjectHeading
        {\textbf{Predicting Time of Prostate Cancer Recurrence} $|$ \emph{University of Alberta}}{Jan. 2023 -- May 2023}
        \resumeItemListStart
          \resumeItem{Developed and evaluated machine learning models (\textbf{Random Survival Forest, Cox, Survival SVM}) in \textbf{Python} to predict prostate cancer recurrence from histopathology images and clinical data. Supervised by Professor Russ Grainer.}
        \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PATENTS-----------
\section{Patents}
\resumeSubHeadingListStart
    \resumeSubheading
      {Systems and Methods for Advanced Content Presentation}{Jun. 2023}
      {U.S. Patent Issued}{Userful Corporation}
\resumeSubHeadingListEnd

\end{document}
